### 2014-05-21 learn_intro.tex
Finish Leslie fixes

\noindent 
\textbf{Only weak evidence of a tradeoff between
  operating range and performance.} We created a RemyCC designed
for a range of networks whose link rates spanned a thousand-fold range
between 1~Mbps and 1000~Mbps, as well as three other protocols that
were more narrowly-targeted at hundred-fold, ten-fold, and two-fold
ranges of link rate (Figure~\ref{fig:breadth}).

>>>>

\noindent 
\textbf{We found weak evidence of a tradeoff between
  operating range and performance.} We created a RemyCC designed
for a range of networks whose link rates spanned a thousand-fold range
between 1~Mbps and 1000~Mbps, as well as three other protocols that
were more narrowly-targeted at hundred-fold, ten-fold, and two-fold
ranges of link rate (Figure~\ref{fig:breadth}).

### 2014-05-21 remy_design.tex
Edit through end
Finish Leslie fixes

\section{How Remy Produces a Congestion-Control Algorithm}
\label{s:design}

The above model may be viewed as a cooperative game that endpoints play. Given
packets to transmit (offered load) at an endpoint, the endpoint must
decide when to send packets in order to maximize its own objective
function. With a particular congestion-control algorithm running on
each endpoint, we can calculate each endpoint's expected score.

@@

Unfortunately, when greater individual throughput is the desired
objective, on a best-effort packet-switched network like the Internet,
it is always advantageous to send a packet. In this setting, if every
endpoint acted rationally in its own self-interest, the resulting Nash
equilibrium would be congestion collapse!\footnote{Other researchers
  have grappled with this problem; for example, Akella et
  al.~\cite{Akella02} studied a restricted game, in which players are
  forced to obey the same particular flavor of TCP, but with the freedom
  to choose their additive-increase and multiplicative-decrease
  coefficients. Even with this constraint, the authors found that the Nash
  equilibrium is inefficient, unless the endpoints are restricted to
  run TCP Reno over a drop-tail buffer, in which case the equilibrium
  is unfair but not inefficient.}  This answer is unsatisfactory from
a protocol-design perspective, when endpoints have the freedom to send
packets when they choose, but the designer wishes to achieve an
efficient and equitable allocation of network capacity.

@@

\item In some RemyCCs, where the goal is operation over a broad range
  of networks, we consider the same feature but with a longer-term
  moving average, using a weight of 1/256 for the newest sample.

@@

\item A lower bound $r > 0$ milliseconds on the time between
  successive sends.

@@

A RemyCC is defined by a set of piecewise-constant \emph{rules}, each
one mapping a rectangular region of the three- or four-dimensional
memory space to a three-dimensional action:
$$
\langle {\tt ack\_ewma}, {\tt send\_ewma}, {\tt rtt\_ratio} \rangle \rightarrow
\langle m, b, r \rangle.
$$

@@

To the best of our knowledge, this dynamic partitioning approach is
novel in the context of multi-agent optimization. The ``greedy''
approach in step 2 is key to the computational tractability and
efficiency of the search because it allows us to prune the search
space. Dividing the memory space into cells of different size
proportional to their activity produces a rule table
whose granularity is finer in regions of higher use.

>>>>

\section{Generating a congestion-control algorithm}
\label{s:design}

The above model may be viewed as a cooperative game that endpoints play. Given
packets to transmit (offered load) at an endpoint, the endpoint must
decide when to send packets in order to maximize the global objective
function. With a particular congestion-control algorithm running on
each endpoint, we can calculate each endpoint's expected score.

@@

Unfortunately, when greater individual throughput is the desired
objective, on a best-effort packet-switched network like the Internet,
it is always advantageous to send a packet. In this setting, if every
endpoint acted rationally in its own self-interest, the resulting Nash
equilibrium would be congestion collapse.\footnote{Other researchers
  have grappled with this problem; for example, Akella et
  al.~\cite{Akella02} studied a restricted game, in which players are
  forced to obey the same particular flavor of TCP, but with the freedom
  to choose their additive-increase and multiplicative-decrease
  coefficients. Even with this constraint, the authors found that the Nash
  equilibrium is inefficient, unless the endpoints are restricted to
  run TCP Reno over a drop-tail buffer, in which case the equilibrium
  is unfair but not inefficient.}  This answer is unsatisfactory from
a protocol-design perspective, when endpoints have the freedom to send
packets when they choose, but the designer wishes to achieve an
efficient and equitable allocation of network capacity.

@@

\item In some RemyCCs, where the goal is operation over a broad range
  of networks, we consider the same feature but with a longer-term
  moving average, using a weight of 1/256 for the newest sample ({\tt
    slow\_ack\_ewma}).

@@

\item A lower bound $\tau > 0$ milliseconds on the time between
  successive sends.

@@

A RemyCC is defined by a set of piecewise-constant \emph{rules}, each
one mapping a rectangular region of the three- or four-dimensional
memory space to a three-dimensional action. For each acknowledgment
received, the RemyCC will update the memory features $\langle {\tt
  ack\_ewma}, {\tt send\_ewma}, {\tt rtt\_ratio}, \{ {\tt
  slow\_ack\_ewma} \} \rangle$ and then execute the corresponding action
$\langle m, b, \tau \rangle$.

@@

%To the best of our knowledge, this dynamic partitioning approach is
%novel in the context of multi-agent optimization. The ``greedy''
%approach in step 2 is key to the computational tractability and
%efficiency of the search because it allows us to prune the search
%space. Dividing the memory space into cells of different size
%proportional to their activity produces a rule table
%whose granularity is finer in regions of higher use.

### 2014-05-21 remy_eval.tex
Finish Leslie fixes

We present the results for the different protocols as {\bf
  throughput-delay plots}, where the log-scale $x$-axis is the
queueing delay (average per-packet delay in excess of minimum
RTT). Lower, better, delays are to the right.  The $y$-axis is the
throughput. Protocols on the ``top right'' are the best on such
plots. We take each individual 100-second run from a simulation as one
point, and then compute the 1-$\sigma$ elliptic contour
of the maximum-likelihood 2D Gaussian distribution that explains the
points. To summarize the whole scheme, we plot the median per-sender
throughput and queueing delay as a circle.

Ellipses that are narrower in the throughput or delay axis correspond
to protocols that are fairer and more consistent in allocating those
quantities. Protocols with large ellipses --- where
identically-positioned users differ widely in experience based on the
luck of the draw or the timing of their entry to the network --- are
less fair. The orientation of an ellipse represents the {\em
  covariance between the throughput and delay} measured for the
protocol; if the throughput were uncorrelated with the queueing delay
(note that we show the queueing delay, not the RTT), the ellipse's
axes would be parallel to the graph's.
Because of the variability and correlations between these quantities
in practice, we believe that such throughput-delay plots are an
instructive way to evaluate congestion-control protocols; they provide
more information than simply reporting mean throughput and delay values.

>>>>

We present the results for the different protocols as {\bf
  throughput-delay plots}, where the log-scale $x$-axis is the
queueing delay (average per-packet delay in excess of minimum
RTT). Lower, better, delays are to the right.  The $y$-axis is the
throughput. Protocols on the top right are the best on such
plots. We take each individual 100-second run from a simulation as one
point, and then compute the 1-$\sigma$ elliptic contour
of the maximum-likelihood 2D Gaussian distribution that explains the
points. To summarize the whole scheme, we plot the median per-sender
throughput and queueing delay as a circle.

Ellipses that are narrower in the throughput or delay axis correspond
to protocols that are more consistent in allocating those
quantities. Protocols with large ellipses are those where
identically-positioned users differ widely in experience based on the
luck of the draw or the timing of their entry to the
network.\footnote{The ellipse represents the variability of the
  results for all nodes across all simulation runs. Thus, the notion
  of ``variability'' here includes both within-run variability or
  fairness (different results for different nodes that compete
  concurrently) as well as variability across runs. In practice, our
  100-second simulation runs were generally long enough, relative to flow
  durations, that the ellipse can be broadly interpreted as
  simply a measure of fairness.} The orientation of an ellipse
represents the {\em covariance between the throughput and delay}
measured for the protocol; if the throughput were uncorrelated with
the queueing delay (note that we show the queueing delay, not the
RTT), the ellipse's axes would be parallel to the graph's.  Because of
the variability and correlations between these quantities in practice,
we believe that such throughput-delay plots are an instructive way to
evaluate congestion-control protocols; they provide more information
than simply reporting mean throughput and delay values.

### 2014-05-21 remy_limits.tex
Finish Leslie fixes

We think this tradeoff is ultimately worth taking: today's endpoints
can execute complex algorithms almost as easily as simple ones, and
with Remy, the bulk of the intelligence is computed offline.

>>>>

We think this tradeoff is ultimately worth taking: today's endpoints
can execute complex algorithms almost as easily as simple ones, and
the \textit{computational} complexity of a RemyCC is low in any event.

### 2014-05-21 remy_model.tex
Finish Leslie fixes

We have typically parametrized networks on three axes: the speed of
bottleneck links, the propagation delay of the network paths, and the
degree of multiplexing, i.e., the number of senders contending for
each bottleneck link. We assume that senders have no control over the
paths taken by their packets to the receiver.

@@

Resource-allocation theories of congestion control have traditionally
employed the alpha-fairness metric to evaluate allocations of
throughput on shared links~\cite{Srikant}. A flow that receives
steady-state throughput of $x$ is assigned a score of $U_\alpha(x) =
\frac{x^{1-\alpha}}{1-\alpha}$. As $\alpha \rightarrow 1$, in the
limit $U_1(x)$ becomes $\log x$.

@@

The flow's score is then 
\begin{equation}
U_\alpha(\textrm{x}) - \delta \cdot U_\beta(\textrm{y}),
\label{eq:util}
\end{equation}
where $\alpha$ and $\beta$ express the fairness-vs.-efficiency
tradeoffs in throughput and delay, respectively, and $\delta$
expresses the relative importance of delay vs.~throughput.% For the
%rest of this paper, we set $\alpha = \beta = 1$ and simply consider
%the sum of $\log(\textrm{throughput}) - \delta \cdot
%\log(\textrm{delay})$ for each flow.

>>>>

We have parametrized networks on four axes: the speed of
bottleneck links, the number of bottlenecks, the propagation delay of the network paths, and the
degree of multiplexing, i.e., the number of senders contending for
each bottleneck link. We assume that senders have no control over the
paths taken by their packets to the receiver.

@@

Resource-allocation theories of congestion control have traditionally
employed the alpha-fairness metric to evaluate allocations of
throughput on shared links~\cite{Srikant}. A flow that receives
steady-state throughput of $x$ is assigned a score of:

\begin{equation*}
U_\alpha(x) = \frac{x^{1-\alpha}}{1-\alpha}
\end{equation*}

As $\alpha \rightarrow 1$, in the limit $U_1(x)$ becomes $\log x$.

@@

The flow's score is then 
\begin{equation*}
U_\alpha(\textrm{x}) - \delta \cdot U_\beta(\textrm{y}),
\label{eq:util}
\end{equation*}
where $\alpha$ and $\beta$ express the fairness-vs.-efficiency
tradeoffs in throughput and delay, respectively, and $\delta$
expresses the relative importance of delay vs.~throughput.% For the
%rest of this paper, we set $\alpha = \beta = 1$ and simply consider
%the sum of $\log(\textrm{throughput}) - \delta \cdot
%\log(\textrm{delay})$ for each flow.
